### 2016-07-06 filters.tex
syntax, new auth notes
privacy notions now give the representation M to the adversary; this was missing before, and the notions did not capture real privacy attacks

In Figure~\ref{fig:fp-filter} we give three distinct notions,
characterized by what access the adversary has to the underlying
hash functions used by the filter.  In the top notion, the hash
functions are secret.  This is the setting addressed by NY, and it
captures applications in which the hash functions are (say) secretly
keyed PRFs, and in which no explicit, external interface to these is
surfaced.
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions
public, but assumes that the adversary only accesses them in a
black-box manner.  That is, the adversary does not exploit
structural features of the hash functions in its attack.  This
notion makes it easy to track the query complexity of an attack, and
also allows us to capture constructions in the random-oracle model.

@@

\heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.  Informally, the adversary's goal is to guess one of the elements of the set~$S$.  Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.  To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{S \getsr \distr{U}{n}:\, x \in S}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.

@@

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}()$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

>>>>

In Figure~\ref{fig:fp-filter} we give three distinct notions,
characterized by what access the adversary has to the underlying
hash functions used by the filter.  In the top notion, the hash
functions are secret.  This is the setting addressed by NY, and it
captures applications in which the hash functions are (say) secretly
keyed PRFs, and in which no explicit, external interface to these is
surfaced.
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions
public, but assumes that the adversary only accesses them in a
black-box manner.  That is, the adversary does not exploit
structural features of the hash functions in its attack.  This
notion makes it easy to track the query complexity of an attack, and
also allows us to capture constructions in the random-oracle model. \tsnote{I'm not sure this is really useful for anything other than ROM analysis.  Perhaps for settings in which the hash-functions are secret, but the attack surface expose a way for the adversary to see their outputs?}

@@

\heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.  Informally, the adversary is given the representation~$M$ of a secret set~$S$, and its goal is to guess one of the elements of~$S$.  Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.  To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{S \getsr \distr{U}{n}:\, x \in S}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.

@@

A weaker notion of privacy would not give~$M$ to the adversary.  However, this would not capture attacks such as those mounted by Neidermayer et al.\cite{XXX}, and would not speak to settings in which (say) an honest-but-curious third party is given the representation~$M$ in order to carry out some task on behalf of the holder of~$S$.

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
$S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(M)$\\
if $x\in S$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle,\HashOracle}(M)$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(i,x)$}\\
Ret $h_i(x)$\\
}
}
%%%%%%%
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
$ S \getsr \distr{U}{n}$\\
$h_1,\ldots,h_k \getsr \Hash$\\
$\HashOracle = (h_1, \ldots, h_k)$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
$x \getsr A^{\QryOracle}(M,\{h_1,h_2,\ldots,h_k\})$\\
if $x\in S$ then Ret 1\\
Ret 0\\
}
%
{
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

### 2016-07-06 intro.tex
privacy notions now give the representation M to the adversary; this was missing before, and the notions did not capture real privacy attacks

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$
(whatever their use) are intended to be kept secret from the
adversary.  Thus, to the extent that it addresses real Bloom filters
at all, the NY security notion only addresses applications in which
the representation is created using secret coins.  But many
real-world applications of Bloom filters have no secrets.  NY point
to web proxies, which use Bloom filters to compactly represent the
objects they store locally, as motivation for their work.  But real
web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their
Bloom filters.  They use the basic Bloom filter with four hash
functions, defined as follows: $h_1(x) =
\mathrm{MD5}(x)[0,\ldots,31]$,
$h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$,
$h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and
$h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no
secrets in the Bloom filters used by Google's BigTable~\cite{xxx},
HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are
applications in which the proposed Bloom filter instantiations do
use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot
g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in
the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
This particular ``encrypted Bloom filter'' instantiation was
suggested for use in efficient linking of records across separate
medical record databases~\cite{xxx}.  (It was subsequently shown not
to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of
frequency analysis recovered the last names of patients given access
only to the Bloom filter array.\tsnote{This shows that
false-positive security and privacy (whatever it is) are orthogonal,
since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
In any case, it is clear that the NY definition does not capture the
most widely used applications of Bloom filters, e.g. CDN summary
caches, P2P network routing algorithms, etc. \tsnote{Could also
point out that their positive results use constructions that have
secret keys, and these are unlikely to be of any use in major
applications like CDNs or P2P networks.  But maybe the horse is
sufficiently beaten by now...}

>>>>

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$
(whatever their use) are intended to be kept secret from the
adversary.  Thus, to the extent that it addresses real Bloom filters
at all, the NY security notion only addresses applications in which
the representation is created using secret coins.  But many
real-world applications of Bloom filters have no secrets.  NY point
to web proxies, which use Bloom filters to compactly represent the
objects they store locally, as motivation for their work.  But real
web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their
Bloom filters.  Squid, in particular, uses the basic Bloom filter with four hash
functions, defined as follows: $h_1(x) =
\mathrm{MD5}(x)[0,\ldots,31]$,
$h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$,
$h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and
$h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no
secrets in the Bloom filters used by Google's BigTable~\cite{xxx},
HBase~\cite{xxx}, \tsnote{make an impressive list.}

There are applications in which the proposed Bloom filter instantiations do
use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot
g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in
the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
This particular ``encrypted Bloom filter'' instantiation was
suggested for use in efficient linking of records across separate
medical record databases~\cite{xxx}.  (It was subsequently shown not
to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of
frequency analysis recovered the last names of patients given access
only to the Bloom filter array.\tsnote{This shows that
false-positive security and privacy (whatever it is) are orthogonal,
since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
In any case, it is clear that the NY definition does not capture the
most widely used applications of Bloom filters, e.g. CDN summary
caches, P2P network routing algorithms, etc. \tsnote{Could also
point out that their positive results use constructions that have
secret keys, and these are unlikely to be of any use in major
applications like CDNs or P2P networks.  But maybe the horse is
sufficiently beaten by now...}
